---
title: "Lab 2"
author: "Your_name_here"
output: html_document
date: "`r Sys.Date()`"
---

# Problem Set: Introduction & Instructions

# Problem 1: Logical Tests on Vectors

1a. Create two vectors, one with values of `1,2,3` and the other with values of `1,2,4`
```{r}
# Create your first vector here


# Create your second vector here


```

1b-e. Run each specified type of logical test between your vectors
```{r}
# 1b. Equality


```
```{r}
# 1c. Inequality


```
```{r}
# 1d. Less than or equal to


```
```{r}
# 1e. Greater than or equal to


```

# Problem 2: Functions

2a-d. Describe what the functions are doing
```{r, eval=FALSE}
# 2a.
vec <- c(1,5,7,2,4, NA)
mean(vec)
```
Answer 2a: 


```{r, eval=FALSE}
# 2b
mean(vec, na.rm=F)
```
Answer 2b:


```{r, eval=FALSE}
# 2c
add <- function(x,y,z){
  return(x+y+7)
}
```
Answer 2c:


```{r, eval=FALSE}
# 2d.
some_function <- function(x,y,z,m){
  c <- mean(c(x,y,z))
  return(c*m)
}
```
Answer 2d:



# Problem 3: More Functions

Create a function that satisfies the requirement(s)

3a. Create a function that takes in two numbers to add them and returns the sum
```{r}

```

3b. Create a function that takes in a number, tests if that number is bigger than 40, and returns the True/False result
```{r}

```

3c. Create a function that takes in a matrix, adds 8 to each element, and returns the new matrix.
```{r}

```

3d. Create a matrix with at least 3 rows and 2 columns. Then, use the function you created in 3c and display the result
```{r}
# Define your matrix here


# Call your 3c function here


```

